### 2020-11-12 Thesis-Chapter5-ThreatModel.tex
Finish spoofing, begin tampering threats

\begin{table}[h]
  \caption{Central Concepts in the \ldawmsr Proposal}
  \label{table-ldawmsr-concepts}
  \begin{FlushLeft}
    \begin{tabular}{ |l|p{6.3cm}|p{6.3cm}| }
      \hline
      \thead{Concept} & \thead{Implementation} & \thead{Outcome} \\ \hline
      Self-escrow
      & The Class key is escrowed in the device's Secure Enclave (or equivalent) using a write-only component; i.e.,
        software can update the key, but only an unexposed hardware interface can read it.
      & Since the Class key itself is being stored, there is no change to the security of the underlying cryptographic
        protocols. Physical possession and partial disassembly is required, which introduces practical barriers to mass
        surveillance.
      \\ \hline
      Time vaulting
      & The hardware interface responds to requests only after proof of sustained possession for a ``lockup period
        (e.g., 72 hours).''
      & The waiting period precludes ``sneak and peak'' attacks and further reduces the utility for mass surveillance.
      \\ \hline
      Authorization
      & After the lockup period, the requestor must provide evidence of authorization. This comes from a shared secret
        between the device and the manufacturer which can be obtained via legal process.
        % Vendor authorization escrow (as opposed to _key_ escrow)
      & Physical possession is now not enough; law enforcement (or attackers) must provide this secret information to
        the device to unlock it.
      \\ \hline
      Transparency
      & In addition to the device disassembly, the escrow agent modifies the device (e.g., burns a fuse) when it has
        been unlocked. The device firmware detects this modification.
      & The device user has evidence that the device has been unlocked, preventing covert usage.
      \\ \hline
    \end{tabular}
  \end{FlushLeft}
\end{table}

@@

The lawful access use case operates as follows: law enforcement obtains a warrant to conduct a search, including the
suspect's mobile device. They obtain the phone, disassemble it to expose the \ac{EA} hardware interface, and begin the
time-vaulted access request. After the lockout period is completed, the device offers its Device ID only. The law
enforcement agency's digital forensics department digitally signs the Device ID and sends it to the device vendor,
alongside the warrant and accompanying proof of legal authorization. The vendor's access compliance department audits
the legal documents and submits the digitally signed Device ID to a secure computing environment such as a Hardware
Security Module. The secure environment authenticates the digital signature, looks up the device's private Device Seal
Key and authorization value, and encrypts them with the law enforcement agency's public key. These encrypted artifacts
are returned to the agency, which decrypts and submits them to the device through the dedicated interface. First is
the authorization value, which is hashed and compared to the stored hash. If that values match, the device accepts and
uses the private Device Seal Key to decrypt the Class key, which was escrowed after being encrypted but the public
Device Seal Key. Once the Class key is decrypted, the escrow agent burns a fuse, and the device is unlocked for forensic
investigation.

@@

@@

\begin{table}[h]
  \caption{Spoofing Threats}
  \label{table-ldawmsr-concepts}
  \begin{FlushLeft}
    \begin{tabular}{ |l|p{2cm}|p{2cm}|p{4.8cm}|p{4.8cm}| }
      \hline
      \thead{ID} & \thead{Identity \\ Spoofed} & \thead{With \\ Respect To} & \thead{Effect} & \thead{Mitigation}
      \\ \hline
      S1 & Device & Officer
      & Planted device to unlock unauthorized device.
      & Require it to be in the forensics department itself.
      \\ \hline
    \end{tabular}
  \end{FlushLeft}
\end{table}

\ii{S1} is Eran Tromer's attack on CLEAR.

@@

>>>>

\begin{table}[h]
  \caption{Central Concepts in the \ldawmsr Proposal}
  \label{table-ldawmsr-concepts}
  \FlushLeft
  \small
  \begin{tabular}{ |l|p{6.3cm}|p{6.3cm}| }
    \hline
    \thead{Concept} & \thead{Implementation} & \thead{Outcome} \\ \hline
    Self-escrow
    & The Class key is escrowed in the device's Secure Enclave (or equivalent) using a write-only component; i.e.,
      software can update the key, but only an unexposed hardware interface can read it.
    & Since the Class key itself is being stored, there is no change to the security of the underlying cryptographic
      protocols. Physical possession and partial disassembly is required, which introduces practical barriers to mass
      surveillance.
    \\ \hline
    Time vaulting
    & The hardware interface responds to requests only after proof of sustained possession for a ``lockup period (e.g.,
      72 hours).''
    & The waiting period precludes ``sneak and peak'' attacks and further reduces the utility for mass surveillance.
    \\ \hline
    Authorization
    & After the lockup period, the requestor must provide evidence of authorization. This comes from a shared secret
      between the device and the manufacturer which can be obtained via legal process.
    & Physical possession is now not enough; law enforcement (or attackers) must provide this secret information to the
      device to unlock it.
    \\ \hline
    Transparency
    & In addition to the device disassembly, the escrow agent modifies the device (e.g., burns a fuse) when it has been
      unlocked. The device firmware detects this modification.
    & The device user has evidence that the device has been unlocked, preventing covert usage.
    \\ \hline
  \end{tabular}
\end{table}

@@

The lawful access use case operates as follows: law enforcement obtains a warrant to conduct a search, including the
suspect's mobile device. They obtain the phone, disassemble it to expose the \ac{EA} hardware interface, and begin the
time-vaulted access request. After the lockout period is completed, the device offers its Device ID only. The law
enforcement agency's digital forensics department digitally signs the Device ID and sends it to the device vendor,
alongside the warrant and accompanying proof of legal authorization. The vendor's access compliance department audits
the legal documents and submits the digitally signed Device ID to a secure computing environment such as a \ac{HSM}. The
secure environment authenticates the digital signature, looks up the device's private Device Seal Key and authorization
token, and encrypts them with the law enforcement agency's public key. These encrypted artifacts are returned to the
agency, which decrypts and submits them to the device through the dedicated interface. First is the authorization token,
which is hashed and compared to the stored hash. If that values match, the device accepts and uses the private Device
Seal Key to decrypt the Class key, which was escrowed after being encrypted but the public Device Seal Key. Once the
Class key is decrypted, the escrow agent burns a fuse, and the device is unlocked for forensic investigation.

This concludes an summarized overview of the system as described in the proposal. However, in a real system, the entire
information lifecycle matters. In order to establish such a system, vendors and law enforcement must establish
mechanisms to populate and update the device and \ac{HSM} key stores and databases. \myfig{fig-dfd-ldawmsr-setup} is a
\ac{DFD} for these scenarios.

\begin{figure}[h!]
  \centering\CaptionFontSize
  \includegraphics[width=0.9\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR-setup.png}
  \caption{The LDAWMSR maintenance data flow diagram.}
  \label{fig-dfd-ldawmsr-setup}
\end{figure}

@@

To save space, the tables use shorthand for law enforcement (LE); law enforcement officer (LEO); law enforcement agency
(LEA); Device ID (DID);

% TODO: Check list of acronyms up to date here ^^

\newcommand{\threattablesettings}{\FlushLeft \small}

\newcommand{\threattablebegin}[3]{
  \begin{FlushLeft}
    \small
    \begin{longtable}{ lp{3cm}p{5.6cm}p{5.6cm} }
      \caption{#1 Threats}
      \label{table-#2}
      \\ \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\ \midrule
      \endfirsthead
      \caption[]{#1 Threats (continued)}
      \\
      \toprule
      \thead{ID} & \thead{#3} & \thead{Effect} & \thead{Mitigation}
      \\
      % \midrule
      \endhead
      \endfoot
      \bottomrule
      \endlastfoot
}

\newcommand{\threattableend}{
    \end{longtable}
  \end{FlushLeft}
}

@@

Spoofing threats are listed in \mytab{table-spoofing}. Notably, \ii{S2} is Eran Tromer's attack \cite{tromer_2018} on
computer scientist Ray Ozzie's related \ac{DAR} \ac{EA} protocol called CLEAR \cite{ozzie_2018}. Savage acknowledges the
influence that CLEAR had on \ldawmsR, and specifically included a note that while this proposal is technically
vulnerable to the same threat, the mitigations listed here would help, and furthermore the likelihood of such an attack
is low and the difficulty high.

\threattablebegin{Spoofing}{spoofing}{Spoof}
  S1 & Device is spoofed to LE via plant
  & Attackers plant a device to get LE to unlock it for them.
  & Require the device to be in the forensics department itself the entire time it is unlocked.
  \\ \hline
  S2 & Device is spoofed to LE via forged DID
  & Attackers rig a device to report a different DID and record the entered unlock artifacts, allowing them into a
    target device.
  & Add a hardware integrity check or alternatively unlock the device in a Faraday cage, extract its data, and destroy
    it.
  \\ \hline
  S3 & LEO is spoofed to LEA
  & Attackers pose as a LEO while the LEA relays back unlock artifacts.
  & Require the device to be in the forensics department itself the entire time it is unlocked.
  \\ \hline
  S4 & LEA is spoofed to vendor during key exchange
  & Attackers pose as an LEA in order to spoof future access requests.
  & Vendor key exchange process involves thorough in-person verification.
  \\ \hline
  S5 & LEA is spoofed to vendor during access request
  & Attackers pose as a LEA and submit an access request. Requires forged legal documents and a stolen LEA private key
    (unless attacker is an insider or has executed a spoofed key exchange).
  & Vendor independently verifies all legal documents. Vendor supports a key revocation and update process that involves
    the same level of in-person verification.
  \\ \hline
  S6 & Manufacturer is spoofed to vendor
  & Attackers pose as the manufacturer to inject malicious data into the DID-Seal database. Must be combined with other
    attacks to be of use.
  & Vendor authenticates data transfers between manufacturing and corporate (does not address a compromised manufacturer
    network or an inside threat).
\threattableend

@@

Tampering threats are listed in \mytab{table-tampering}.

\threattablebegin{Tampering}{tampering}{Tamper}
  T1 & Defensive user corrupts DSK, DID, or token
  & LE attempts at perform \ac{EA} will fail due to corrupt data. Requires compromise of the Secure Enclave or advanced
    hardware manipulation tools.
  & Since these values are known at manufacturing time and never change, they can be made read-only. (The symmetric key
    variant of \ldawmsr requires updating the symmetric equivalent of the public DSK, and is therefore more vulnerable
    to this threat.)
  \\ \hline
  T2 & Defensive user destroys the \ac{EA} hardware interface
  & LE attempts at perform \ac{EA} will fail due to damaged hardware.
  & Manufacture the device to require destructive disassembly to access the interface. This increases the cost
    associated with deploying and using the system.
  \\ \hline
  T3 & LE insider tampers with DID before digital signature
  & .
  & .
\threattableend
